Topic Scores

### 2019-02-27 Topic Scores.Rmd
.DS_Store and empty line
minor changes to make code more interactive

##Getting applied (gamma and beta) 
```{r getting beta and gamma}
# k=10, 20, 35
beta_description <- lapply(
  LDA_model,
  get_beta
)

@@

```
##Inspect topics
```{r inspect topics}
topics <- beta_description$k35 %>%
  group_by(topic) %>%
  top_n(10, beta)

@@

student <- list()
student$kw_policy <- c("international", "economic", "conflict", "develop", "policy", "war", "philosophy") #sample(terms, 5)
student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable") #sample(terms, 5)
```

##getting top courses per student
```{r topic score student}
student$topic_score <- beta_description$k35 %>%
  filter(term %in% student$kw_policy)       %>%
  group_by(topic)                           %>% #maybe we can do this with transcripts afterwards
  summarize(B_score= sum(beta))             %>%
  ungroup()                                 %>%
  mutate(Total_b      = sum(B_score),
         B_proportion = B_score/Total_b)    %>%
  arrange(desc(B_score))

@@

student$course_score <- gamma_descriptions$k35     %>%
  full_join(student$topic_score, by = "topic")     %>%
  mutate(X = gamma * B_proportion)                 %>%
  group_by(document)                               %>%
  summarise(course_score = sum(X))                 %>%
  arrange(desc(course_score))                      %>%
  left_join(
    select(d_course, `Course ID`, `Course Title`),
    by = c("document" = "Course ID")
    )
```

>>>>

##Getting applied (gamma and beta) 
```{r getting beta and gamma}
# k=10, 20, 35
beta_description <- lapply(
  clean_models,
  get_beta
)

@@

```
##Inspect topics
```{r inspect topics}
topics <- clean_models$beta_distribution$k10 %>%
  group_by(topic) %>%
  top_n(10, beta)

@@

student <- list()
student$kw_policy <- c("international", "economic", "conflict", "develop", "policy", "war", "philosophy")
student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable")
```

##getting top courses per student
```{r topic score student}
student$topic_score <- clean_models$beta_distribution$k35 %>%
  filter(term %in% student$kw_climate)       %>%
  group_by(topic)                           %>% #maybe we can do this with transcripts afterwards
  summarize(B_score= sum(beta))             %>%
  ungroup()                                 %>%
  mutate(Total_b      = sum(B_score),
         B_proportion = B_score/Total_b)    %>%
  arrange(desc(B_score)) %>%
  print

@@

student$course_score <- clean_models$gamma_distribution$k35     %>%
  full_join(student$topic_score, by = "topic")     %>%
  mutate(X = gamma * B_proportion)                 %>%
  group_by(document)                               %>%
  summarise(course_score = sum(X))                 %>%
  arrange(desc(course_score))                      %>%
  left_join(
    select(d_course, `Course ID`, `Course Title`),
    by = c("document" = "Course ID")
    ) %>%
  print
```
